\chapter{Introduction}

Social media is ubiquitous in our daily lives, providing users with a platform to connect online, share content, and build communities \cite{ishaq2023design}. When interacting with other people's posts on the internet, users may experience a wide range of emotions, including frustration, excitement, joy, and dejection \cite{tanna2020sentiment}. As the number of people using social media has grown over time, social media applications have become a very common aspect of using the internet \cite{aichner2021twenty}. When users share online content to educate other users about global events, social media applications can be used very effectively \cite{yu2022social}. Social media applications also assist businesses in expanding by offering online services to meet the needs of their clients \cite{go2016but}.

\section{Background}
Over time, people's methods of exchanging information and content have changed, and social media platforms like Facebook and YouTube have had a lasting impact on society \cite{komito2011social}. Social media have been promoted as a means of fostering human connections and enabling communication. Social media gives users the ability to search for other profiles, have a public profile, and a list of other users they are connected to \cite{leist2013social}. People of all ages can now interact with friends, family, the educational system, and society through social media \cite{wilkinson2015social}. A billion users share content and information online via social media platforms like Facebook, YouTube, Twitter, and Instagram \cite{wilkinson2015social}.

Modern web applications are responsive and fast. This development for web apps has allowed users to have a smooth experience. Users expect to have fun while surfing the web, and this is what makes social media comfortable for so many users. Users can connect with important people and things that matter when a website offers them quality features that make them feel good, and that's exactly what the Internet has become. When the internet began, changes were made to web technologies such as HTML, CSS, React, Express, Node and JavaScript in order to create the best possible website for users \cite{aryal2020mern}.

\section{Motivation}
This project aims to build a social media platform that securely creates user engagement through features such as posts, likes and comments. Developing numerous advanced features to design an engaging and easy to use social media platform. User engagement is about how someone feels about the content that is presented on the page, which can show strong positive engagement \cite{shahbaznezhad2021role}. A successful social media platform must have diverse content and offer the opportunity to spread content to a very large audience of site visitors \cite{khan2017social}. A social media platform should focus on information consumption at a deeper level by looking at engagement in the form of likes, dislikes, comments, shares, uploads and views in a way or another \cite{khan2017social}.

The social media application uses the web technologies such as React, MongoDB, Express and Node to create a platform where users can stay active while interacting with the social platform. Web technologies are growing rapidly, and MERN full stack is popular for handling the front-end and back-end with the help of JavaScript support on the client side and server side \cite{aryal2020mern}. 

\section{Objectives}
\begin{enumerate}
  \item To enhance user engagement through the implementations of features such as posts, likes, dislikes ,images, and user interactions.
  \item Create a secure user authentication using token-based methods user login and registrations.
  \item Dynamic content support for updating and deleting user-generated posts.  
  \item Allow users to follow and unfollow other users on the platform. A recommendation system to help users get started on following a user.
   \item A Search functionality for users to search others by username with responsive search results.
   \item A user profiles for showing important details and follower counts.
   \item Learn and develop best practices using various
   technologies in the MERN stack. 
   \item Gain project building skills.
\end{enumerate}

\section{Problem Domain}
Developing a social media platform is all about managing with the expectation of users of this generation where the influence of the Internet's is very powerful. The integral parts that social media should provide are the sharing different forms of information for the users to interact and engage, with likes and comments \cite{go2016but}. A community is created for users to enjoy. Companies are very careful to select and connect features of social media applications, such as expression and sharing, to create a growing community \cite{go2016but}. In today's world, social media is an important modern form of communication, connecting so many people and creating a different ways of interaction, including sharing opinions, images and messages. 

Social media is accessible so that users can use it for free with complete privacy protection, social media has preferences that allow users to make updates according to their preferences, and social media has a reach that allows websites to gain a global audience \cite{agarwal2010information}. There are challenges and opportunities to overcome when creating a user-oriented social media platform that offers different preferences and features. The most common challenges are securing user privacy, implementing user authentication, handling dynamic content, and making the environment engaging and interactive for the user to enjoy. 

\section{Project Overview}
This dissertation displays the development of a dynamic and user-oriented social media platform called ConnectSphere. The aim is to build an engaging digital space to enhance user interaction. The project aims to create a pleasant social media experience, ensuring seamless and responsive platform for users to enjoy, share, connect and communicate.

The MERN stack is used for the project objectives, combining both the front-end and back-end technologies. The front-end is built using React, a JavaScript library for creating user interfaces, and Material-UI guarantees responsive styling of components. The back-end is built using Node.js for the server-side development, ensuring stability and efficiency. Express.js, a framework for Node, which simplifies server side development code. MongoDB is used as a database and provides a way to store and retrieve data. JSON web token provides a secure user authentication, improving the platform's security. Security is a key aspect for a social media platform. Redux toolkit is used for state management. This social media platform focuses on providing various features to enhance the social media experience. Users are encouraged to interact, fostering a dynamic and responsive community. The technologies used in this project, helps creates a social media platform, providing users with a secure and engaging online community.